---
title: "Model Essentials: correlations b/w random terms"
output:
  html_document:
    css: css/sidebar.css
    keep_md: yes
    toc: yes
---



<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  fig.width = 6.5, 
  fig.height = 4, 
  fig.path = 'figure_study/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./reports/basic/2_basic_study_report.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load_sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load_packages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare_globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak_data, echo=echoChunks, results='show', message=FALSE}
```

```{r missing_studies, echo=echoChunks, results='hide', message=FALSE}
```


```{r prepare_pretty, echo=echoChunks, results='hide', message=FALSE}
```

This report tabulates pivotal results to the workshop's research agenda: correlations between  random intercepts, slopes, and residuals in each bivariate model. For available combinations of constructs and measures in bivariate models [Model Counts](http://htmlpreview.github.io/?https://github.com/IALSA/IALSA-2015-Portland/blob/master/reports/counts.html)



# Predictor legend

Models differ with respect to the covariate variables, entered as fixed effects on the second level. Abbreviations used in the tables are as follows: 

- **empty** -- no covariate included into the model
- **a** -- age (at baseline)
- **ae** -- age + education
- **aeh** -- age + education + height
- **aehplus** -- age + education + height + diabetes + smoking history + cardiovascular
- **full** -- all covariate availible in the study (will differ by study)

# Study-Specific Tables

```{r study_tables, echo=echoChunks, message=TRUE, results='asis'}
```



# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
