---
title: 'BISR: pulmonary (full)'
output:
  word_document:
    toc: no
  html_document:
    keep_md: no
    toc: yes
date: 'Date: `r Sys.Date()`'
---

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results    = 'show', 
  comment    = NA, 
  tidy       = FALSE,
  fig.width  = 4, 
  fig.height = 4, 
  fig.path   = 'figure-png/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./reports/correlation-3/correlation-3-pc.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

```{r input-phys-cog, echo=echoChunks, results='show', message=FALSE}
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE, warning =FALSE}
```

```{r formatting-functions, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```


```{r select-outcome, echo=echoChunks, message=TRUE,eval=TRUE}
# track <- "grip"
# track <- "gait"
track <- "pulmonary"
```


```{r select-data, echo=echoChunks, message=TRUE,eval=TRUE}
```


## Legend

- `Cov(Slopes)` = raw covariance  
- `Corr(Slopes)Est` = correlation , ESTimated in Mplus  
- `CI(Slopes)Est` = Confidence intervals estimated in Mplus  
- `Corr(Slopes)Comp` = correlation, computed outside of Mplus using Fisher's transform 

Note: cases in which restricted (co)variances or insufficient decimals prevent the computation of correlations are marked by `---`

**Raw covariance** and **estimated correlations** are reported in the form : **`est(se) pval star`**,where         
- `est` is the covariance estimate on the original metric   
- `se` is the standard error on the original metric  
- `pval` is the p-value associated with the raw covariance  
- `star` is significance indicator associated with corresponding covariance estimate, with  `.`, `*`, `**`, and `***` indicating significance at `.10`, `.05`, `.01`, and `.001` alpha levels, respectively

**Confidence intervals** for estimated correlations are reported in the form: **`(low,high)`**,where   
- `low` - bottom boundry of the 95% confidence interval
- `high` - top boundry of the 95% confidence interval

**Computed correlations** are reported in the form: **`est(low, high)`**, where      
- `est` is the correlation coefficient computed from raw (co)variances using Fisher transfrom   
- `low` and `high` are the 95% confidence intervals associated with the computed correlations  



```{r table-static-full, echo=echoChunks, message=TRUE, results='asis', eval=T}
```

```{r table-static-focus, echo=echoChunks, message=TRUE, results='asis', eval=F}
```




# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session-info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
