---
title: "Model Counts: IALSA Portland 2015"
output:
  html_document:
    css: css/sidebar.css
    keep_md: yes
    toc: yes
---



<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  fig.width = 6.5, 
  fig.height = 4, 
  fig.path = 'figure_study/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./scripts/2_individual_study_report.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load_sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load_packages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare_globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Frequency counts   -->

This report tabulates frequency counts of bivariate models that are available in the workshop collective at the current time. For correlations between random terms in bivariate models consult [Model Essentials](http://htmlpreview.github.io/?https://github.com/IALSA/IALSA-2015-Portland/blob/master/reports/essentials.html)

## Overview

We are yet to receive model results from the following studies:  
```{r missing_studies, echo=echoChunks, results='asis', message=FALSE}
```


Presently, the **total number of legally named models** supplied by the participating studies is
```{r number_studies, echo=echoChunks, results='asis', message=FALSE}
```
: they include both *bivariate* and *univariate* models. Strings *"nophys"* and *"nocog"*, imply that the model is univariate (e.i. nocog == The particular cog predictor is "none")

<!-- Frequency counts   -->
Counting valid models in each study:
```{r freq_studies, echo=echoChunks, results='show', message=FALSE}
```

# Physcial Domain

## Constructs 

Number of models that use the following **Physical contructs**
```{r freq_phys_constructs_studies, echo=echoChunks, results='show', message=FALSE}
```

## Measures

Number of models that use the following **Physical measures**
```{r freq_phys_measures_studies, echo=echoChunks, results='show', message=FALSE}
```

## Measures by Constructs

Number of models using this **measure** of the  physical **construct**
```{r freq_phys_measures_phys_construct, echo=echoChunks, results='show', message=FALSE}
```

## Measures by Constructs and Studies

Number of models using this **measure** of the  physical **construct**, by study
```{r freq_phys_measures_phys_construct_studies, echo=echoChunks, results='show', message=FALSE}
```


# Cognitive Domain

## Constructs 

Number of models that use the following **Cognitive contructs**
```{r freq_cog_constructs_studies, echo=echoChunks, results='show', message=FALSE}
```

## Measures

Number of models that use the following **Cognitive measures**
```{r freq_cog_measures_studies, echo=echoChunks, results='show', message=FALSE}
```

## Measures by Constructs

Number of models using this **measure** of the  cognitive **construct**
```{r freq_cog_measures_cog_construct, echo=echoChunks, results='show', message=FALSE}
```

## Measures by Constructs and Studies

Number of models using this **measure** of the  cognitive **construct**, by study
```{r freq_cog_measures_cog_construct_studies, echo=echoChunks, results='show', message=FALSE}
```







# Bivariate models

## Cross Constructs

Number of models that uses this **physical construct** (column) and  **cognitive construct** (row):
```{r freq_cog_construct_phys_construct, echo=echoChunks, results='show', message=FALSE}
```
It is important to remember that these numbers reflect only the combinations of **constructs**, the  **operationalizations** of these construct (specifc outcomes) that may differ from model to model. 

## Cross Measures

Number of models that uses this **physical measure** (column) and  **cognitive measure** (row):
```{r freq_cog_measure_phys_measure, echo=echoChunks, results='show', message=FALSE}
```

## Cross Measures (fill)

```{r freq_cog_measure_phys_measure_studies_allnames, echo=echoChunks, results='show', message=FALSE}
```


## Cross Measures by Study

```{r freq_cog_measure_phys_measure_studies, echo=echoChunks, results='asis', message=FALSE}
```






# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
