---
title: "FScore Scatters"
output:
  html_document:
    css: ~/GitHub/IALSA-2015-Portland/libs/css/sidebar.css
    keep_md: yes
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 8, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/physical/fscores_scatter/fscores_scatter.R") 
```



<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load_packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load_sources, echo=echoChunks, message=TRUE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare_globals, echo=echoChunks, results='show', message=FALSE}
```

```{r get_gh5_files, echo=echoChunks, results='show', message=FALSE}
```


<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Basic table view.   -->
```{r basic_table, echo=TRUE, results='show', message=FALSE}
```

<!-- Basic graph view.   -->
```{r basic_graph, echo=TRUE, results='show', message=FALSE}
```

```{r get_pair_data, echo=TRUE, results='show', message=FALSE}
```

```{r basic_graph_1, echo=FALSE, results='show', message=FALSE, fig.width=8, fig.height=11}
```
#FEMALES
# EAS
## grip_pef
```{r eas_female_aehplus_grip_pef, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pef_gait
```{r eas_female_aehplus_pef_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_gait
```{r eas_female_aehplus_grip_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

# HRS
## grip_gait
```{r hrs_female_aehplus_grip_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_pef
```{r hrs_female_aehplus_grip_pef, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pef_gait
```{r hrs_female_aehplus_pef_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```


# LASA
## gait_grip
```{r lasa_female_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_gait
```{r lasa_female_aehplus_pek_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_grip
```{r lasa_female_aehplus_pek_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```



# OCTO
## gait_grip
```{r octo_female_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_gait
```{r octo_female_aehplus_pek_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_grip
```{r octo_female_aehplus_pek_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```


# RADC
## fev_gait
```{r radc_female_aehplus_fev_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## fev_grip
```{r radc_female_aehplus_fev_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## gait_grip
```{r radc_female_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```


# SATSA
## gait_fev
```{r satsa_female_aehplus_gait_fev, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## gait_grip
```{r satsa_female_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_fev
```{r satsa_female_aehplus_grip_fev, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

#MALES
# EAS
## grip_pef
```{r eas_male_aehplus_grip_pef, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pef_gait
```{r eas_male_aehplus_pef_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_gait
```{r eas_male_aehplus_grip_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

# HRS
## grip_gait
```{r hrs_male_aehplus_grip_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_pef
```{r hrs_male_aehplus_grip_pef, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_pef
```{r hrs_male_aehplus_grip_pef, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```


# LASA
## gait_grip
```{r lasa_male_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_gait
```{r lasa_male_aehplus_pek_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_grip
```{r lasa_male_aehplus_pek_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```



# OCTO
## gait_grip
```{r octo_male_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_gait
```{r octo_male_aehplus_pek_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## pek_grip
```{r octo_male_aehplus_pek_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```


# RADC
## fev_gait
```{r radc_male_aehplus_fev_gait, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## fev_grip
```{r radc_male_aehplus_fev_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## gait_grip
```{r radc_male_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```


# SATSA
## gait_fev
```{r satsa_male_aehplus_gait_fev, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## gait_grip
```{r satsa_male_aehplus_gait_grip, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```

## grip_fev
```{r satsa_male_aehplus_grip_fev, echo=TRUE, results='show', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
```



