---
title: 'BISR: pulmonary'
output:
  html_document:
    css: ~/GitHub/IALSA-2015-Portland/libs/css/sidebar-simple-wide.css
    toc: yes
  word_document:
    toc: no
date: 'Date: `r Sys.Date()`'
---

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results    = 'show', 
  comment    = NA, 
  tidy       = FALSE,
  fig.width  = 12, 
  fig.height = 7, 
  out.width = "1400px",
  dpi = 100,
  fig.path   = 'figure-png/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./reports/domain-map/cognitive-domain-map.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE, warning =FALSE}
```

```{r create-assist-ds, echo=echoChunks, results='show', message=FALSE, warning =FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

```{r graphing-settings, echo=echoChunks, results='hide', message=FALSE, warning =FALSE}
```

```{r define-densing-functions, echo=echoChunks, results='hide', message=FALSE, warning =FALSE}
```

```{r define-graphing-functions, echo=echoChunks, results='hide', message=FALSE, warning =FALSE}
```

```{r assemble-dense-displays, echo=echoChunks, results='hide', message=FALSE, warning =FALSE}
```

```{r select-pulmonary, echo=echoChunks, message=TRUE, eval=T}
```

# Legend

- `Covariance` is raw covariance  
- `Correlaton` is correlation estimated in _Mplus_, displayed with standard error 
- `Correlation(CI)` is correlation estimated in _Mplus_ displayed with 95% confidence intervals 
- `Fisher(CI)` is correlation, computed from raw (co)variances through Fisher transform

***Note***: cases in which restricted (co)variances or insufficient decimals prevent the computation of Fisher(CI) are marked by `---`

`Covariance` and `Correlation` are given in the format` est(se) pval star`, where     

- `est` is the point estimate     
- `se` is the standard error   
- `pval` is the p-value   
- `star` is the indicator of statistical significance associated with corresponding point estimate, where  `.`, `*`, `**`, and `***` indicate significance at `.10`, `.05`, `.01`, and `.001` alpha levels respectively.  

`Correlation(CI)` and `Fisher(CI)` are given in the format `est(low,high) star`, where  

- `est` is the point estimate     
- `low` is the bottom boundry of the 95% confidence interval  
- `high` is the top boundry of the 95% confidence interval  
- `star` is the indicator of statistical significance associated with corresponding point estimate, where  `.`, `*`, `**`, and `***` indicate significance at `.10`, `.05`, `.01`, and `.001` alpha levels respectively.  

***Note***: For `Fisher(CI)`the p-value associated with the correlation coefficient **CANNOT** be computed, as the underlying distribution of the parameter cannot be assumed normal. Instead, we list the p-value associated with the raw covariance of the respective term.  


```{r print-domain-map, echo=echoChunks, results='asis', message=TRUE}
```



# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session-info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
