---
title: 'BISR: gait'
output:
  word_document:
    toc: no
  html_document:
    keep_md: yes
    toc: yes
date: 'Date: `r Sys.Date()`'
---

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results    = 'show', 
  comment    = NA, 
  tidy       = FALSE,
  fig.width  = 4, 
  fig.height = 4, 
  fig.path   = 'figure-png/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./reports/correlation-2/correlation-2.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE, warning =FALSE}
```

```{r formatting-functions, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```


```{r select-grip, echo=echoChunks, message=TRUE,eval=T}
```


```{r table-dynamic, echo=echoChunks, message=TRUE,eval=F}
```

The table reports the model of type 'aehplus', which include covariates *a*ge, *e*ducation, *h*eight, and binary covariates smoking history, cardiovascular disease, and diabetes. 

The table reports relationships between levels, slopes, and residuals between the two processes in a given pair of outcomes. For each index, we report the raw covariances produced by the Mplus estimation routine and the correlations with confidence intevals, computed from the estimated (co)variances using Fisher's transform.

Raw covariance are reported in the form : ` est(se) pval`     
where      
- `est` is the covariance estimate on the original metric   
- `se` is the standard error on the original metric  
- `pval` is the p-value associated with the raw covariance  

Computed correlations are reported in the form: ` est(low, high) star`   
where      
- `est` is the correlation coefficient computed from raw (co)variances using Fisher transfrom   
- `low` and `high` are the 95% confidence intervals associated with the computed correlations  
- `star` is significance indicator associated with corresponding covariance estimate, with  `.`, `*`, `**`, and `***` indicating significance at `.10`, `.05`, `.01`, and `.001` alpha levels, respectively

Note: cases in which restricted (co)variances or insufficient decimals prevent the computation of correlations are marked by `---`

```{r table-static-2, echo=echoChunks, message=TRUE, results='asis'}
```



# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session-info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
